---
title: "rugby-try-analysis"
author: "Joshua Waugh"
date: "09/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This document describes the exploratory analysis conducted on data relatied to try-scoring in the 2017 Super Rugby competition.

This data consists of tries that were scored during the 2017 Super Rugby competition (observation/rows). Here is a description:

1. `try_no`: a unique identification number given to each try
2. `round_no`: an identification number to distinguish the round number the try was scored in
3. `attacking_team`: the try-scoring team
4. `defending_team`: the opposition team who conceded the try
5. `attacking_rank`: the final league ranking at the end of the season of the try-scoring team
6. `defending_rank`: the final league ranking at the end of the season of the opposition team
7. `attacking_conference`: the conference group of the try-scoring team
8. `defending_conference`: the conference group of the opposition team
9. `game_time`: the game time in minutes when the try was scored
10. `try_source`: the initial source of possession for the attacking team preceding the try
11. `final_source`: the event that directly preceded the try and resulted in the try being scored
phases: the total number of phases between gaining possession, and the try being scored (a phase is from one ruck to the next ruck)
12. `time_from_source`: the time taken from gaining possession to scoring the try, in seconds
13. `possession_zone`: the zone on the field the attacking team gained possession of the ball before scoring the try (A = attacking 22m line to try-line, B = halfway to attacking 22m line, C = defensive 22m line to halfway, D = )
14. `offloads`: the number of offloads from gaining possession to the try being scored
15. `passes`: the number of passes from gaining possession to the try being scored
16. `total_passes`: the number of offloads plus passes

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
